Online supplemental material of the article:\\ \vspace{7mm} 'Hilbert space approximate Bayesian Gaussian processes using Stan'\\ \vspace{7mm} Case Studies

### 2020-04-10 Paper/online_supplemental_material/online_material.tex
update online material

\begin{table}
\begin{center}
\begin{tabular}{|c|*{6}{c|}}\hline
\backslashbox{\small Estimate}{\small True} & \multicolumn{1}{p{1cm}|}{\centering k = 1} &  \multicolumn{1}{p{1cm}|}{\centering k = 2} & \multicolumn{1}{p{1.5cm}|}{\centering k = 3} & \multicolumn{1}{p{1cm}|}{\centering k = 4} & \multicolumn{1}{p{1cm}|}{\centering k = 5} & \multicolumn{1}{p{1cm}|}{\centering } \\ 
\hline \multicolumn{1}{|p{3cm}|}{ \centering k = 1} &90&39&14&3&11&42\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 2} &46&301&8&2&3&16\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 3}  &8&4&59&4&1&19\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 4}  &5&2&6&342&5&5\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 5}  &8&2&1&0&38&19\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering }  &42\%&13\%&32\%&2\%&34\%&$\textbf{17\%}$\\
\hline
\end{tabular}
\end{center}
\caption{Confusion matrix after the Q-fold cross-validation procedure over the training data.}
  \label{ch5_tab_parcels}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|c|*{6}{c|}}\hline
\backslashbox{\small Estimate}{\small True} & \multicolumn{1}{p{1cm}|}{\centering k = 1} &  \multicolumn{1}{p{1cm}|}{\centering k = 2} & \multicolumn{1}{p{1cm}|}{\centering k = 3} & \multicolumn{1}{p{1cm}|}{\centering k = 4} & \multicolumn{1}{p{1cm}|}{\centering k = 5} & \multicolumn{1}{p{1cm}|}{\centering } \\ 
\hline \multicolumn{1}{|p{3cm}|}{ \centering k = 1} &90&39&14&3&11&42\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 2} &46&301&8&2&3&16\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 3}  &8&4&59&4&1&19\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 4}  &5&2&6&342&5&5\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering k = 5}  &8&2&1&0&38&19\%\\
\hline \multicolumn{1}{|p{3cm}|}{\centering }  &42\%&13\%&32\%&2\%&34\%&$\textbf{17\%}$\\
\hline
\end{tabular}
\end{center}
\caption{Confusion matrix after the Q-fold cross-validation procedure over the training data.}
  \label{ch5_tab_parcels}
\end{table}
